---
title: "Evaluatie zorgprogramma hartfalen"
author: "Willem Raat"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(readxl)
library(lubridate)

# read in the dataframes
df.bnp <- read_excel("C:\\Users\\u0124654\\Google Drive\\Doctoraat\\Projecten\\Zorgprogramma HF Leuven\\dataverwerking\\huisartsenfeedback\\ntprobnp.xlsx", col_names = TRUE)
df.gp <- read_excel("C:\\Users\\u0124654\\Google Drive\\Doctoraat\\Projecten\\Zorgprogramma HF Leuven\\dataverwerking\\huisartsenfeedback\\huisartsen.xlsx", col_names = TRUE)
df.ed <- read_excel("C:\\Users\\u0124654\\Google Drive\\Doctoraat\\Projecten\\Zorgprogramma HF Leuven\\dataverwerking\\huisartsenfeedback\\educaties.xlsx", col_names = TRUE)

# clean up the bnp dataframe
df.bnp <- df.bnp%>%
  select(datum, naam, praktijk)%>%
  ## parse datetime column
  mutate(datum = ymd(datum))%>%
  ## clean name column %>%
  mutate(naam = str_trim(naam))%>%
  mutate(naam = str_to_title(naam))%>%
  ## make a second praktijkcolumn based on the name column for each practice and the participating physicians
  mutate(praktijkcode = case_when(
    naam %in% c("Hauwaerts","Persoons", "Plu", "Roelofs", "Van Muysen", "Vanderhaegen", "Verle") ~ "1",
    naam %in% c("Aertgeerts","De Ceulaer", "De Cock", "Dewyspelaere", "Vander Mijnsbrugge", "Vliers") ~ "2",
    naam %in% c("Bertheloot","Deneffe", "Descamps", "Lisaerde", "Smeulders", "Verbakel") ~ "3",
    naam %in% c("De Aguirre","Degelin", "Gils", "Pollers", "Sterckx", "Van Acoleyen", "Van Decraen", "Wouters") ~ "4",
    naam %in% c("Dijckmans","Ghesquiere") ~ "5",
    naam %in% c("Beke","Pacolet", "Radoes", "Van Pelt", "Van Wouwe", "Vanysacker") ~ "6",
    naam %in% c("Arnalsteen","De Sutter", "Foley", "Maertens", "Maes", "Vanhoren") ~ "7",
    naam %in% c("De Lille","Van Heden", "Van Pottelbergh") ~ "8",
    naam %in% c("Delmeiren","Janssens", "Milants", "Pint", "Verscheure") ~ "9",
    naam %in% c("Empsen","Libert", "Longin", "Spileers", "Tange", "Uyttebroeck", "Van Damme", "Van Den Bergh", "Van Den Eede", "Van Der Mullen") ~ "10",
    naam %in% c("Boeve","Buelens", "Lemlijn", "Michielsen", "Soubotko", "Van Hulle", "Walder") ~ "11",
    naam %in% c("Burvenich","Mannaerts", "Spaey", "Wesemael") ~ "12",
    naam %in% c("Kiekens", "Groot", "Himpens", "Luyten", "Vanderstappen") ~ "13",
    naam %in% c("Beerwerth","Deraeve", "Erkens", "Van Goethem") ~ "14",
    naam %in% c("De Knijf","Dierickx", "Lenaerts", "Schoenmakers", "Van Baelen", "Van Boxem", "Van Mechelen", "Van Raemdonck") ~ "15",
    naam %in% c("Bartholomeeusen","Bervoets", "Brankaer", "De Dycker", "Duquet", "Genevrois", "Hiele", "Jespers", "Rijnders") ~ "16",
    naam %in% c("Nous","De Groote") ~ "17",
    naam %in% c("Butaye") ~ "18",
    naam %in% c("Loos", "Schoonheere", "Smeets", "Vanhaverbeke") ~ "19",
    TRUE ~ "0"))

df.bnp <- df.bnp%>%
  mutate(praktijkcode = as.factor(praktijkcode))

# clean up the educations dataset
df.ed <- df.ed%>%
  mutate(aanmeldingsbron = as.factor(aanmeldingsbron))%>%
  mutate(opmerking = replace_na(opmerking, "geen"))%>%
  mutate(opmerking = str_trim(opmerking))%>%
  mutate(praktijkcode = case_when(
    opmerking == "minnepoort" ~ "5",
    opmerking == "butaye" ~ "18",
    TRUE ~ "" 
  ))%>%
  select(datum, aanmeldingsbron, praktijkcode)%>%
  mutate(bron = case_when(
    aanmeldingsbron == "hh" ~ "Heilig Hart",
    aanmeldingsbron == "uzl" ~ "UZ Leuven",
    aanmeldingsbron == "ha" ~ "Huisarts",
    TRUE ~ ""
  ))%>%
  select(-aanmeldingsbron)%>%
  mutate(datum = as_date(datum))%>%
  mutate(bron = as.factor(bron))%>%
  mutate(bron = fct_relevel(bron, "Heilig Hart", "UZ Leuven", "Huisarts", ""))

# Next create a number of variables in different steps to include in the later process rapport
## Step 1. create the interval period indicating the interval between dmp start and current date
startdate <- ymd("2020-01-01")
enddate <- ymd(Sys.Date())
timespan <- interval(start = startdate, end = Sys.Date())
interval.m <- time_length(timespan, unit ="month")

## Step 2. create arguments defining the total number of gp's in the program and for each practice
total.gp <- nrow(distinct(df.gp))

total.gp1 <- nrow(distinct(filter(df.gp, praktijkcode ==1)))
total.gp2 <- nrow(distinct(filter(df.gp, praktijkcode ==2)))
total.gp3 <- nrow(distinct(filter(df.gp, praktijkcode ==3)))
total.gp4 <- nrow(distinct(filter(df.gp, praktijkcode ==4)))
total.gp5 <- nrow(distinct(filter(df.gp, praktijkcode ==5)))
total.gp6 <- nrow(distinct(filter(df.gp, praktijkcode ==6)))
total.gp7 <- nrow(distinct(filter(df.gp, praktijkcode ==7)))
total.gp8 <- nrow(distinct(filter(df.gp, praktijkcode ==8)))
total.gp9 <- nrow(distinct(filter(df.gp, praktijkcode ==9)))
total.gp10 <- nrow(distinct(filter(df.gp, praktijkcode ==10)))
total.gp11 <- nrow(distinct(filter(df.gp, praktijkcode ==11)))
total.gp12 <- nrow(distinct(filter(df.gp, praktijkcode ==12)))
total.gp13 <- nrow(distinct(filter(df.gp, praktijkcode ==13)))
total.gp14 <- nrow(distinct(filter(df.gp, praktijkcode ==14)))
total.gp15 <- nrow(distinct(filter(df.gp, praktijkcode ==15)))
total.gp16 <- nrow(distinct(filter(df.gp, praktijkcode ==16)))
total.gp17 <- nrow(distinct(filter(df.gp, praktijkcode ==17)))
total.gp18 <- nrow(distinct(filter(df.gp, praktijkcode ==18)))

## Step 3. define the total number of unique GPs who prescribed a test and total degree of participation and for each practice separately
unique.gp.bnp <- nrow(distinct(as.tibble(df.bnp$naam)))

unique.gp.bnp1 <- nrow(distinct(filter(df.bnp, praktijkcode == 1), naam))
unique.gp.bnp2 <- nrow(distinct(filter(df.bnp, praktijkcode == 2), naam))
unique.gp.bnp3 <- nrow(distinct(filter(df.bnp, praktijkcode == 3), naam))
unique.gp.bnp4 <- nrow(distinct(filter(df.bnp, praktijkcode == 4), naam))
unique.gp.bnp5 <- nrow(distinct(filter(df.bnp, praktijkcode == 5), naam))
unique.gp.bnp6 <- nrow(distinct(filter(df.bnp, praktijkcode == 6), naam))
unique.gp.bnp7 <- nrow(distinct(filter(df.bnp, praktijkcode == 7), naam))
unique.gp.bnp8 <- nrow(distinct(filter(df.bnp, praktijkcode == 8), naam))
unique.gp.bnp9 <- nrow(distinct(filter(df.bnp, praktijkcode == 9), naam))
unique.gp.bnp10 <- nrow(distinct(filter(df.bnp, praktijkcode == 10), naam))
unique.gp.bnp11 <- nrow(distinct(filter(df.bnp, praktijkcode == 11), naam))
unique.gp.bnp12 <- nrow(distinct(filter(df.bnp, praktijkcode == 12), naam))
unique.gp.bnp13 <- nrow(distinct(filter(df.bnp, praktijkcode == 13), naam))
unique.gp.bnp14 <- nrow(distinct(filter(df.bnp, praktijkcode == 14), naam))
unique.gp.bnp15 <- nrow(distinct(filter(df.bnp, praktijkcode == 15), naam))
unique.gp.bnp16 <- nrow(distinct(filter(df.bnp, praktijkcode == 16), naam))
unique.gp.bnp17 <- nrow(distinct(filter(df.bnp, praktijkcode == 17), naam))
unique.gp.bnp18 <- nrow(distinct(filter(df.bnp, praktijkcode == 18), naam))

participation.bnp <- round(unique.gp.bnp/total.gp, 3)*100

participation.bnp1 <- round(unique.gp.bnp1/total.gp1, 3)*100
participation.bnp2 <- round(unique.gp.bnp1/total.gp2, 3)*100
participation.bnp3 <- round(unique.gp.bnp1/total.gp3, 3)*100
participation.bnp4 <- round(unique.gp.bnp1/total.gp4, 3)*100
participation.bnp5 <- round(unique.gp.bnp1/total.gp5, 3)*100
participation.bnp6 <- round(unique.gp.bnp1/total.gp6, 3)*100
participation.bnp7 <- round(unique.gp.bnp1/total.gp7, 3)*100
participation.bnp8 <- round(unique.gp.bnp1/total.gp8, 3)*100
participation.bnp9 <- round(unique.gp.bnp1/total.gp9, 3)*100
participation.bnp10 <- round(unique.gp.bnp1/total.gp10, 3)*100
participation.bnp11 <- round(unique.gp.bnp1/total.gp11, 3)*100
participation.bnp12 <- round(unique.gp.bnp1/total.gp12, 3)*100
participation.bnp13 <- round(unique.gp.bnp1/total.gp13, 3)*100
participation.bnp14 <- round(unique.gp.bnp1/total.gp14, 3)*100
participation.bnp15 <- round(unique.gp.bnp1/total.gp15, 3)*100
participation.bnp16 <- round(unique.gp.bnp1/total.gp16, 3)*100
participation.bnp17 <- round(unique.gp.bnp1/total.gp17, 3)*100
participation.bnp18 <- round(unique.gp.bnp1/total.gp18, 3)*100

## Step 4. define the median number of tests per prescribing GP and for each practice separately
median.bnp <- as.numeric(df.bnp
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))

median.bnp1 <- as.numeric(df.bnp%>%filter(praktijkcode == 1)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp2 <- as.numeric(df.bnp%>%filter(praktijkcode == 2)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp3 <- as.numeric(df.bnp%>%filter(praktijkcode == 3)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp4 <- as.numeric(df.bnp%>%filter(praktijkcode == 4)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp5 <- as.numeric(df.bnp%>%filter(praktijkcode == 5)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp6 <- as.numeric(df.bnp%>%filter(praktijkcode == 6)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp7 <- as.numeric(df.bnp%>%filter(praktijkcode == 7)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp8 <- as.numeric(df.bnp%>%filter(praktijkcode == 8)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp9 <- as.numeric(df.bnp%>%filter(praktijkcode == 9)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp10 <- as.numeric(df.bnp%>%filter(praktijkcode == 10)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp11 <- as.numeric(df.bnp%>%filter(praktijkcode == 11)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp12 <- as.numeric(df.bnp%>%filter(praktijkcode == 12)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp13 <- as.numeric(df.bnp%>%filter(praktijkcode == 13)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp14 <- as.numeric(df.bnp%>%filter(praktijkcode == 14)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp15 <- as.numeric(df.bnp%>%filter(praktijkcode == 15)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp16 <- as.numeric(df.bnp%>%filter(praktijkcode == 16)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp17 <- as.numeric(df.bnp%>%filter(praktijkcode == 17)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))
median.bnp18 <- as.numeric(df.bnp%>%filter(praktijkcode == 18)
                         %>%group_by(naam)
                         %>%summarize(aantal = n())
                         %>%summarize(median = median(aantal)))

## Step 5. define the number of monthly tests generally and for each practice
total.tests <- nrow(df.bnp)

total.tests1 <- nrow(filter(df.bnp, praktijkcode ==1))
total.tests2 <- nrow(filter(df.bnp, praktijkcode ==2))
total.tests3 <- nrow(filter(df.bnp, praktijkcode ==3))
total.tests4 <- nrow(filter(df.bnp, praktijkcode ==4))
total.tests5 <- nrow(filter(df.bnp, praktijkcode ==5))
total.tests6 <- nrow(filter(df.bnp, praktijkcode ==6))
total.tests7 <- nrow(filter(df.bnp, praktijkcode ==7))
total.tests8 <- nrow(filter(df.bnp, praktijkcode ==8))
total.tests9 <- nrow(filter(df.bnp, praktijkcode ==9))
total.tests10 <- nrow(filter(df.bnp, praktijkcode ==10))
total.tests11 <- nrow(filter(df.bnp, praktijkcode ==11))
total.tests12 <- nrow(filter(df.bnp, praktijkcode ==12))
total.tests13 <- nrow(filter(df.bnp, praktijkcode ==13))
total.tests14 <- nrow(filter(df.bnp, praktijkcode ==14))
total.tests15 <- nrow(filter(df.bnp, praktijkcode ==15))
total.tests16 <- nrow(filter(df.bnp, praktijkcode ==16))
total.tests17 <- nrow(filter(df.bnp, praktijkcode ==17))
total.tests18 <- nrow(filter(df.bnp, praktijkcode ==18))

monthly.tests <- round(total.tests/interval.m, 2)

monthly.tests1 <- round(total.tests1/interval.m, 2)
monthly.tests2 <- round(total.tests2/interval.m, 2)
monthly.tests3 <- round(total.tests3/interval.m, 2)
monthly.tests4 <- round(total.tests4/interval.m, 2)
monthly.tests5 <- round(total.tests5/interval.m, 2)
monthly.tests6 <- round(total.tests6/interval.m, 2)
monthly.tests7 <- round(total.tests7/interval.m, 2)
monthly.tests8 <- round(total.tests8/interval.m, 2)
monthly.tests9 <- round(total.tests9/interval.m, 2)
monthly.tests10 <- round(total.tests10/interval.m, 2)
monthly.tests11 <- round(total.tests11/interval.m, 2)
monthly.tests12 <- round(total.tests12/interval.m, 2)
monthly.tests13 <- round(total.tests13/interval.m, 2)
monthly.tests14 <- round(total.tests14/interval.m, 2)
monthly.tests15 <- round(total.tests15/interval.m, 2)
monthly.tests16 <- round(total.tests16/interval.m, 2)
monthly.tests17 <- round(total.tests17/interval.m, 2)
monthly.tests18 <- round(total.tests18/interval.m, 2)

# Step 6. Calculate the total number of educations by GPs and for each practice separately

total.ed.gp <- nrow(filter(df.ed, bron == "Huisarts"))

total.ed.gp1 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 1))
total.ed.gp2 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 2))
total.ed.gp3 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 3))
total.ed.gp4 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 4))
total.ed.gp5 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 5))
total.ed.gp6 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 6))
total.ed.gp7 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 7))
total.ed.gp8 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 8))
total.ed.gp9 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 9))
total.ed.gp10 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 10))
total.ed.gp11 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 11))
total.ed.gp12 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 12))
total.ed.gp13 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 13))
total.ed.gp14 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 14))
total.ed.gp15 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 15))
total.ed.gp16 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 16))
total.ed.gp17 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 17))
total.ed.gp18 <- nrow(filter(df.ed, bron == "Huisarts"& praktijkcode == 18))

```

# Inleiding

In dit rapport vindt u een kort overzicht van de interventies van het Leuvense zorgprogramma hartfalen en van uw eigen implementatieproces.

# NT-proBNP
## Algemeen
```{r, echo = FALSE, message = FALSE}
# transform the dataset to include the sum total of NT-proBNPs per month per practice
df.bnp2 <- df.bnp%>%
  group_by(maand = floor_date(datum, "month"), praktijkcode)%>%
  summarize(count = n())

df.bnp3 <- df.bnp%>%
  group_by(maand = floor_date(datum, "month"))%>%
  summarize(count = n())

```


Tussen januari 2020 en `r format(Sys.time(), '%B %Y')` werden er `r nrow(df.bnp)` NT-proBNP testen afgenomen. Het maandgemiddelde was `r round(mean(df.bnp3$count))` testen. Onderstaande grafiek geeft een overzicht van het aantal testen per deelnemende praktijk.

```{r, echo = FALSE}
ggplot(df.bnp2, aes(x = maand, y = count, fill = praktijkcode)) +
  geom_bar(stat = "identity", position = "stack", show.legend = FALSE, alpha = 0.8, colour = "black") +
  theme_minimal() +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  labs(x = "Maand",
       y = "Totaal") +
  scale_fill_viridis_d()

```

# Educaties
## Algemeen
```{r, echo = FALSE, message = FALSE}
# transform the ed dataset to include sum total of educations per month
df.ed2 <- df.ed%>%
  filter(bron != "")%>%
  group_by(maand = floor_date(datum, "month"), bron)%>%
  summarize(count = n())

df.ed3 <- df.ed%>%
  group_by(maand = floor_date(datum, "month"))%>%
  summarize(count = n())
```

Tussen januari 2020 en `r format(Sys.time(), '%B %Y')` werden er `r nrow(df.ed)` educaties uitgevoerd. Het maandgemiddelde was `r round(mean(df.ed3$count))` educaties. Onderstaande grafiek geeft een overzicht van het aantal educaties per deelnemende praktijk.

```{r, echo = FALSE}
ggplot(df.ed2, aes(x = maand, y = count, fill = bron)) +
  geom_bar(stat = "identity", position = "stack", show.legend = TRUE, alpha = 0.8, colour = "black") +
  theme_minimal() +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  labs(x = "Maand",
       y = "Totaal") +
  scale_fill_viridis_d()

```
